Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-03-01 src/article.tex
Description of scaffolder problem in background

These methods provide a wide variety of possible approaches for scaffolding
a genome. The scaffold may still however require manual editing and addition of
sequence if computational methods are not completely successful. This involves
moving and joining larges blocks of nucleotide text together by hand which may
be error-prone and precludes any reproducibility. \pb

\subsection*{Overview} %{{{2

The software outlined here, ``Scaffolder'', is aimed at creating a syntax and
software framework for producing and editing a genome scaffold. Scaffolder uses
a specific file format to define how contigs are joined, additional sequences
inserted, and for the specification of unknown regions. This syntax allows
a scaffold to be updated by simply editing the scaffold file and allows the
scaffolding process to be both reproducible and deterministic. \pb

>>>>

These methods provide a wide array of approaches for scaffolding contigs into
a continious super-sequence. The scaffolding process may still however require
joining and addition of sequence by hand in the case manually derived
scaffolding data such as through PCR. This intermediate manual stage in the
scaffolding process involves moving and joining larges blocks of nucleotide
text together by hand which may be error-prone and precludes any
reproducibility. \pb

The software outlined here, ``Scaffolder'', aims to solve this problem by
creating at creating a syntax and software framework for producing and editing
a genome scaffold. Scaffolder uses a specific file format to define how contigs
are joined, additional sequences inserted, and for the specification of unknown
regions. This syntax allows a scaffold to be updated by simply editing the
scaffold file wich allows the scaffolding process to be both reproducible and
provides a concise overview of how the scaffold was constructed. \pb
